\bf \texttt{forestecology} package for modeling interspecies competition between trees

### 2021-01-09 etc/paper/forestecology.Rmd
Amplified ideas in abstract

1. set the context for and purpose of the work 
1. indicate the approach and the methods 
1. outline the main results 
1. identify the conclusions and wider implications

>>>>

1. Set the context for and purpose of the work: The scientific question/problem and the desiderata
    + fitting models for interspecific competition and assessing them using spatial crossvalidation
    + Leverage ForestGEO protocols providing standardization
1. Indicate the approach and the methods: Use tidyverse, simple features, and tidymodels packages. 
    + tidyverse: as stated in tidy tools manifesto: standadized data structures, functional programming with pipe, designed for humans
    + sf: tidyverse-friendly package that makes wrangling and visualizing spatial data much easier
    + tidymodels: given our spatial-crossvalidation, use tidymodels framework is a collection of packages for modeling and machine learning using tidyverse principles
1. Outline the main results: We replicate from scratch the figure in PLOSOne paper using Big Woods data, conduct similar analysis for SCBI data.
    + Code would've been way more complicated in base. 
    + We don't have to worry about how the component functions work, only that sequence/converyor belt is correct and output is correct.
    + Scientist is abstracted away from ugly programming details.
1. Identify the conclusions and wider implications:
    + New scientific conclusions from SCBI data
    + this can serve as blue print for other modeling situations.
    + Modularly switch out our bayesian lm() functions to anything you want.

### 2021-01-09 etc/paper/forestecology.tex
Amplified ideas in abstract

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  set the context for and purpose of the work: models for interspecific
  competition. Robert and spatial crossvalidation
\item
  indicate the approach and the methods: use tidyverse, sf, and
  tidymodels packages.
\item
  outline the main results: Recreate the figure in PLOSOne paper. Code
  would've been way more complicated in base. We don't have to worry
  about how the component functions work, only that sequence/converyor
  belt is correct and output is correct. scientist is abstracted away
  from ugly programming details.
\item
  identify the conclusions and wider implications: the fact truths hold
  was already covered in PLOSOne paper, this package implements this and
  can serve as a blueprint for others who model
\end{enumerate}

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Set the context for and purpose of the work: The scientific
  question/problem and the desiderata

  \begin{itemize}
  \tightlist
  \item
    fitting models for interspecific competition and assessing them
    using spatial crossvalidation
  \item
    Leverage ForestGEO protocols providing standardization
  \end{itemize}
\item
  Indicate the approach and the methods: Use tidyverse, simple features,
  and tidymodels packages.

  \begin{itemize}
  \tightlist
  \item
    tidyverse: as stated in tidy tools manifesto: standadized data
    structures, functional programming with pipe, designed for humans
  \item
    sf: tidyverse-friendly package that makes wrangling and visualizing
    spatial data much easier
  \item
    tidymodels: given our spatial-crossvalidation, use tidymodels
    framework is a collection of packages for modeling and machine
    learning using tidyverse principles
  \end{itemize}
\item
  Outline the main results: We replicate from scratch the figure in
  PLOSOne paper using Big Woods data, conduct similar analysis for SCBI
  data.

  \begin{itemize}
  \tightlist
  \item
    Code would've been way more complicated in base.
  \item
    We don't have to worry about how the component functions work, only
    that sequence/converyor belt is correct and output is correct.
  \item
    Scientist is abstracted away from ugly programming details.
  \end{itemize}
\item
  Identify the conclusions and wider implications:

  \begin{itemize}
  \tightlist
  \item
    New scientific conclusions from SCBI data
  \item
    this can serve as blue print for other modeling situations.
  \item
    Modularly switch out our bayesian lm() functions to anything you
    want.
  \end{itemize}
\end{enumerate}
